Solar jet observed at the limb in SDO/SST

### 2016-04-06 paper/ms_temp_paper.tex
begin work on time distance section

\section{Results}

\subsection{Time Distance Evolution}
Let us begin with the evolution of the jet feature over time.

\section{Discussion}

>>>>

\section{Results & Discussion}

\subsection{Time Distance Evolution}
Let us begin with the evolution of the jet-like feature over time. 
We have utilised a self-built, manual feature measuring tool, which, uses a clicking mechanism to select the foot and tip of the macrospicule, calculates the half weight and uses this as a guide to measure the width of the feature.
Using this tool on each frame, and therefore the time cadence of the instrument, we obtain the evolution of the jet and general ballistic information.
We have used this tool on each wavelength to examine the extent upwards through the corona.
